---
title: "Eating Out"
author: "Diego Martinez"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The data comes from the 1998 General Social Survey answer this question

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
GSS <-read.dta(file="GSS1998.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```

## Methods 

The response variable is categorical. Which is, did you dine out last week? The explanatory variable is race: another categorical variable. The reponse variavle fits under yes or no thus, it's categorical. For race, we know from past experience that it is for sure a categorical variable. So we use cat~cat. Thus, we'll a chi squared test and a fisher exact test. The inferential test will be done by the chi squared test & the fisher exact test. 





